\documentclass[11pt, letterpaper]{article}
\usepackage[margin=0.8in, top=0.5in, bottom=0.8in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdftitle={CV - Yichao Jin - Computational Social Science \& AI},
}

\begin{document}
\thispagestyle{empty}
\pagestyle{empty}

% HEADER
\begin{center}
    {\huge \textbf{Yichao Jin, Ph.D.}} \\
    \vspace{0.5em}
    School of Economic, Political and Policy Sciences \\
    The University of Texas at Dallas, Richardson, TX 75080 \\
    \vspace{0.5em}
    \href{https://yichao2022.github.io}{\textbf{https://yichao2022.github.io}} \quad | \quad \href{https://orcid.org/0009-0003-7667-5143}{\textbf{ORCID}} \quad | \quad \href{mailto:Yichao.Jin@UTDallas.edu}{Yichao.Jin@UTDallas.edu} \\
    \vspace{0.5em}
    \textit{Computational Social Science \;|\; Behavioral AI \;|\; Structural Causal Modeling \;|\; Causal Inference}
\end{center}

\vspace{0.5em}
\noindent\hrulefill

\section*{Education}
\textbf{University of Texas at Dallas} \hfill May 2026 \\
\textbf{Ph.D. in Public Policy and Political Economy}
\begin{itemize}[noitemsep, topsep=0pt, label={-}]
    \item Dissertation: ``Intertemporal Choice in Vaccination Timing: Evidence from a Discrete Choice Experiment in Wuhan'' --- \href{https://www.proquest.com/docview/3354986484}{\textbf{ProQuest}}
    \item Committee: Dohyeong Kim (Chair), Richard Scotch, Soyoung Kwon, Khai Chiong.
    \item Dean of Graduate Education Dissertation Research Award (2025).
\end{itemize}

\vspace{0.5em}
\noindent \textbf{University of Texas at Dallas} \hfill May 2026 \\
\textbf{M.S. in Social Data Analytics and Research}

\vspace{0.5em}
\noindent \textbf{University of Queensland} \hfill 2019 \\
\textbf{Master of Development Economics}

\vspace{0.5em}
\noindent \textbf{University of California, Riverside} \hfill 2017 \\
\textbf{B.A. in Economics}

\section*{Research Agenda}
My research develops causally-constrained AI agents for behavioral simulation and policy analysis. I integrate discrete choice experiments, structural causal modeling, and large language models to build Behavioral Digital Twins---empirically-grounded synthetic agents that generate behavior within estimated human choice frontiers rather than from LLM training priors. This framework enables pre-screening of behavioral interventions and policy designs before field deployment, with applications to health behavior, education, and social policy.

\section*{Working Papers}
\begin{enumerate}
    \item \textbf{``Empirical-Frontier Regularization for LLM Synthetic Agents: A Preference-Anchored Framework''} \\
    \textit{Working Paper (Target: J. Biomedical Informatics)} --- \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=6686418}{\textbf{SSRN Link}}. Introduces a DCE-grounded empirical-frontier regularization framework for LLM synthetic agents. Using a convex anchoring rule, the Static-BDT Anchor reduces waiting-time monotonicity violations from 62.5\% to 4.2\% and improves Spearman rank correlation from $-$0.024 to 0.952. Presented at DAISY 2026 (ACM CHIL 2026) and AIxPH 2026.

    \item \textbf{``Value Contamination in Policy Simulation: Measuring How LLM Policy-Value Orientations Shape Predicted Administrative Burden Effects''} \\
    \textit{Target: Journal of Computational Social Science} --- \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=6876161}{\textbf{SSRN Link}}. Audit framework measuring value sensitivity in LLM-generated policy simulations. Tests nine LLMs across six model families through policy-value orientation batteries, narrative frame-decomposition, and within-model frame-manipulation experiments (N=2,160 observations).

    \item \textbf{``Waiting Time as a Behavioral Barrier to Vaccination Uptake: Nonlinear Heterogeneity by Institutional Trust''} \\
    \textit{Under Review at Economic Analysis and Policy} --- \href{https://yichao2022.github.io/jmp.pdf}{\textbf{Link to Full Draft}}. Structural DCE framework measuring interaction between temporal barriers and institutional trust in vaccination decisions.

    \item \textbf{``The Price of Waiting: Evidence on Cash--Time Trade-Offs in Vaccination Time Discount''} \\
    \textit{Manuscript in Preparation (Expected submission: August 2026)}.
\end{enumerate}

\section*{Research Experience \& Affiliations}
\textbf{Doctoral Researcher, Spatial Health AI Research Partnership (SHARP), UT Dallas} \\
\begin{itemize}[noitemsep, topsep=0pt, label={-}]
    \item Leading interdisciplinary research on the intersection of artificial intelligence, geospatial analytics, and health policy.
    \item Managing large-scale datasets and developing computational simulations (R, Python) to evaluate pandemic preparedness.
    \item Leading development of the Behavioral Digital Twin (BDT) framework, integrating DCE data with causally-constrained LLM agents for synthetic policy simulation.
\end{itemize}

\vspace{0.5em}
\noindent \textbf{Graduate Researcher, Behavioral Health Economics Laboratory, UT Dallas} \\
\begin{itemize}[noitemsep, topsep=0pt, label={-}]
    \item Conducted high-salience behavioral experiments (N=1,027) analyzing risk-weighted health decisions and institutional trust.
\end{itemize}

\section*{Conference Presentations}
\begin{itemize}[noitemsep, topsep=0pt]
    \item \textbf{AIxPH 2026 (1st Annual Conference on AI and Public Health, Baltimore, MD)}: Empirical-Frontier Regularization for LLM Synthetic Agents — Poster Presentation.
    \item \textbf{DAISY 2026 Workshop at ACM Conference on Health, Inference, and Learning (CHIL) 2026}: Behavioral Digital Twins --- A Causally-Faithful Generative Framework.
    \item \textbf{APPAM Fall Research Conference 2025} (Seattle, WA): Estimating Time Discount Rate for Vaccination.
    \item \textbf{UT Dallas Graduate Research Symposium 2025}: Modeling Vaccination Decisions with Hyperbolic Discounting.
\end{itemize}

\section*{Technical Skills \& Certifications}
\textbf{Econometrics:} Mixed Logit (MXL), Latent Class Models (LCM), SEIR Modeling, Causal Inference. \\
\textbf{AI \& ML:} PyTorch, Transformers (HuggingFace), LLM APIs (OpenAI, Anthropic), LangChain, Causal Machine Learning. \\
\textbf{Software:} Stata (Advanced), R, Python, MATLAB, LaTeX, SQL, GIS. \\
\textbf{Certifications:} Stanford Artificial Intelligence Graduate Certificate; CITI Human Subjects Protection.

\section*{Honors \& Awards}
\begin{itemize}[noitemsep, topsep=0pt]
    \item \textbf{2025} Dean of Graduate Education Dissertation Research Award, UT Dallas
    \item \textbf{2025} Betty \& Gifford Johnson Graduate Travel Award, UT Dallas
    \item \textbf{2016} Omicron Delta Epsilon, International Honor Society for Economics
\end{itemize}

\vspace{1em}
\noindent\hrulefill
\begin{center}
    \textbf{REFERENCES}
\end{center}

\begin{minipage}[t]{0.48\textwidth}
    \raggedright
    \textbf{\href{https://profiles.utdallas.edu/dohyeong.kim}{\textcolor{blue}{Dohyeong Kim (Chair)}}} \\
    University of Texas at Dallas \\
    Senior Associate Dean of Graduate Education \\
    Robert E. Holmes Jr. Professor of Public Policy, GIS \& Social Data Analytics \\
    Team Lead, SHARP \\
    \href{mailto:dohyeong.kim@utdallas.edu}{\textcolor{blue}{dohyeong.kim@utdallas.edu}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
    \raggedright
    \textbf{\href{https://profiles.utdallas.edu/soyoung.kwon}{\textcolor{blue}{Soyoung Kwon}}} \\
    Associate Professor of Sociology and Public Health \\
    Editorial Board, \textit{Society and Mental Health} \\
    University of Texas at Dallas \\
    \href{mailto:soyoung.kwon@utdallas.edu}{\textcolor{blue}{soyoung.kwon@utdallas.edu}}
\end{minipage}

\vspace{1.5em}

\begin{minipage}[t]{0.48\textwidth}
    \raggedright
    \textbf{\href{https://profiles.utdallas.edu/richard.scotch}{\textcolor{blue}{Richard Scotch}}} \\
    Professor Emeritus of Sociology, \\
    Public Health, and Public Policy \\
    University of Texas at Dallas \\
    \href{mailto:richard.scotch@utdallas.edu}{\textcolor{blue}{richard.scotch@utdallas.edu}}
\end{minipage}

\vspace{1em}
\begin{center}
    \textit{Last Updated: July 2026}
\end{center}

\end{document}
