\documentclass[11pt, letterpaper]{article}
\usepackage[margin=0.8in, top=0.5in, bottom=0.8in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    pdftitle={CV - Yichao Jin - Health Policy \& Economics},
}

\begin{document}
\thispagestyle{empty}
\pagestyle{empty}

% HEADER
\begin{center}
    {\huge \textbf{Yichao Jin, Ph.D.}} \\
    \vspace{0.5em}
    School of Economic, Political and Policy Sciences \\
    The University of Texas at Dallas, Richardson, TX 75080 \\
    \vspace{0.5em}
    \href{https://yichao2022.github.io}{\textbf{https://yichao2022.github.io}} \quad | \quad \href{https://orcid.org/0009-0003-7667-5143}{\textbf{ORCID}} \quad | \quad \href{mailto:Yichao.Jin@UTDallas.edu}{Yichao.Jin@UTDallas.edu} \\
    \vspace{0.5em}
    \textit{Health Economics \;|\; Health Policy \;|\; Applied Econometrics \;|\; Causal Inference}
\end{center}

\vspace{0.5em}
\noindent\hrulefill

\section*{Education}
\textbf{University of Texas at Dallas} \hfill May 2026 \\
\textbf{Ph.D. in Public Policy and Political Economy}
\begin{itemize}[noitemsep, topsep=0pt, label={-}]
    \item Dissertation: ``Intertemporal Choice in Vaccination Timing: Evidence from a Discrete Choice Experiment in Wuhan'' --- \href{https://www.proquest.com/docview/32574920}{\textbf{ProQuest}}
    \item Committee: Dohyeong Kim (Chair), Richard Scotch, Soyoung Kwon, Khai Chiong.
    \item Dean of Graduate Education Dissertation Research Award (2025).
\end{itemize}

\vspace{0.5em}
\noindent \textbf{University of Texas at Dallas} \hfill May 2026 \\
\textbf{M.S. in Social Data Analytics and Research}

\vspace{0.5em}
\noindent \textbf{University of Queensland} \hfill 2019 \\
\textbf{Master of Development Economics}

\vspace{0.5em}
\noindent \textbf{University of California, Riverside} \hfill 2017 \\
\textbf{B.A. in Economics}

\section*{Research Agenda}
My research applies structural econometric methods to study how institutional design, regulatory incentives, and behavioral constraints shape health outcomes and policy effectiveness. I integrate discrete choice experiments, causal inference, and large-scale data analysis to evaluate how individuals and providers respond to policy changes. My work spans health behavior, health system performance, and the interaction between regulatory oversight and market outcomes.

\section*{Working Papers}
\begin{enumerate}
    \item \textbf{``Waiting Time as a Behavioral Barrier to Vaccination Uptake: Nonlinear Heterogeneity by Institutional Trust''} \\
    \textit{Under Review at Economic Analysis and Policy} --- \href{https://yichao2022.github.io/jmp.pdf}{\textbf{Link to Full Draft}}
    \begin{itemize}[noitemsep, topsep=0pt]
        \item Structural econometric analysis of how institutional trust moderates the effect of time costs on health service utilization.
        \item Identifies heterogeneous treatment effects relevant for targeting policy interventions across subpopulations.
    \end{itemize}

    \item \textbf{``Empirical-Frontier Regularization for LLM Synthetic Agents''} \\
    \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=6686418}{\textbf{SSRN Link}}. Three-stage framework integrating DCE data and causal constraints to align generative agents with empirical choice frontiers, achieving 93\% reduction in frontier-deviation error. Presented at AIE Summer Conference 2026 and DAISY 2026 (ACM CHIL 2026).

    \item \textbf{``Value Contamination in Policy Simulation''} \\
    \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=6876161}{\textbf{SSRN Link}}. Audit framework measuring how model-inherent value orientations distort LLM-generated policy simulations.

    \item \textbf{``The Price of Waiting: Evidence on Cash--Time Trade-Offs in Vaccination Time Discount''} \\
    \textit{Manuscript in Preparation (Expected submission: August 2026)} --- Targeting \textit{Social Science \& Medicine}.
\end{enumerate}

\section*{Research Experience \& Affiliations}
\textbf{Doctoral Researcher, Spatial Health AI Research Partnership (SHARP), UT Dallas} \\
\begin{itemize}[noitemsep, topsep=0pt, label={-}]
    \item Leading interdisciplinary research on the intersection of artificial intelligence, geospatial analytics, and health policy.
    \item Managing large-scale datasets and developing computational simulations (R, Python) to evaluate pandemic preparedness.
    \item Leading development of the Behavioral Digital Twin (BDT) framework, integrating DCE data with causally-constrained LLM agents for synthetic policy simulation.
\end{itemize}

\vspace{0.5em}
\noindent \textbf{Graduate Researcher, Behavioral Health Economics Laboratory, UT Dallas} \\
\begin{itemize}[noitemsep, topsep=0pt, label={-}]
    \item Conducted high-salience behavioral experiments (N=1,027) analyzing risk-weighted health decisions and institutional trust.
\end{itemize}

\section*{Conference Presentations}
\begin{itemize}[noitemsep, topsep=0pt]
    \item \textbf{AI and Economics (AIE) Summer Conference 2026}: Empirical-Frontier Regularization for LLM Synthetic Agents.
    \item \textbf{APPAM Fall Research Conference 2025} (Seattle, WA): Estimating Time Discount Rate for Vaccination.
    \item \textbf{DAISY 2026 Workshop at ACM Conference on Health, Inference, and Learning (CHIL) 2026}: Behavioral Digital Twins --- A Causally-Faithful Generative Framework.
    \item \textbf{UT Dallas Graduate Research Symposium 2025}: Modeling Vaccination Decisions with Hyperbolic Discounting.
\end{itemize}

\section*{Technical Skills \& Certifications}
\textbf{Econometrics:} Mixed Logit (MXL), Latent Class Models (LCM), SEIR Modeling, Causal Inference. \\
\textbf{AI \& ML:} PyTorch, Transformers (HuggingFace), LLM APIs (OpenAI, Anthropic), LangChain, Causal Machine Learning. \\
\textbf{Software:} Stata (Advanced), R, Python, MATLAB, LaTeX, SQL, GIS. \\
\textbf{Certifications:} Stanford Artificial Intelligence Graduate Certificate; CITI Human Subjects Protection.

\section*{Honors \& Awards}
\begin{itemize}[noitemsep, topsep=0pt]
    \item \textbf{2025} Dean of Graduate Education Dissertation Research Award, UT Dallas
    \item \textbf{2025} Betty \& Gifford Johnson Graduate Travel Award, UT Dallas
    \item \textbf{2016} Omicron Delta Epsilon, International Honor Society for Economics
\end{itemize}

\vspace{1em}
\noindent\hrulefill
\begin{center}
    \textbf{REFERENCES}
\end{center}

\begin{minipage}[t]{0.48\textwidth}
    \raggedright
    \textbf{\href{https://profiles.utdallas.edu/dohyeong.kim}{\textcolor{blue}{Dohyeong Kim (Chair)}}} \\
    University of Texas at Dallas \\
    Senior Associate Dean of Graduate Education \\
    Robert E. Holmes Jr. Professor of Public Policy, GIS \& Social Data Analytics \\
    Team Lead, SHARP \\
    \href{mailto:dohyeong.kim@utdallas.edu}{\textcolor{blue}{dohyeong.kim@utdallas.edu}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
    \raggedright
    \textbf{\href{https://profiles.utdallas.edu/soyoung.kwon}{\textcolor{blue}{Soyoung Kwon}}} \\
    Associate Professor of Sociology and Public Health \\
    Editorial Board, \textit{Society and Mental Health} \\
    University of Texas at Dallas \\
    \href{mailto:soyoung.kwon@utdallas.edu}{\textcolor{blue}{soyoung.kwon@utdallas.edu}}
\end{minipage}

\vspace{1.5em}

\begin{minipage}[t]{0.48\textwidth}
    \raggedright
    \textbf{\href{https://profiles.utdallas.edu/richard.scotch}{\textcolor{blue}{Richard Scotch}}} \\
    Professor Emeritus of Sociology, \\
    Public Health, and Public Policy \\
    University of Texas at Dallas \\
    \href{mailto:richard.scotch@utdallas.edu}{\textcolor{blue}{richard.scotch@utdallas.edu}}
\end{minipage}

\vspace{1em}
\begin{center}
    \textit{Last Updated: June 2026}
\end{center}

\end{document}
